Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-26 paper.tex

Architectures showing reduced system complexity will greatly
facilitate the implementation effort towards robust interactions
which, in turn, have a positive impact on characteristics such as
gateway predictability, transparence, general reliability and results
traceability and reproducibility; characteristics that are also key to
a good user experience. \closednote{Marc-Etienne}{I find that
  something is weak in this last paragraph. Robustness will help with
  transparency, sure, but it seems only a small facet.  Also, the text
  seem to timidly favor architectures with less
  components/interactions without much explanation... Complex systems
  can be robust, but at greater costs...  Here is one: "Architectures
  showing reduced system complexity will greatly facilitate the
  implementation effort towards robust interactions which, in turn,
  have a positive impact on characteristics such as gateway
  predictability, transparence, general reliability and results
  traceability and reproducibility; characteristics that are also key
  to a good user experience."}{Tristan}{Agreed, fixed as suggested.}

@@

Finally, the particular technical or historical context of a science
gateway project may obviously influence the choice of an architecture
to integrate workflow engines. For instance, some workflow engines may
be already available as web services, which would tend to favor
service invocation, and other science gateways may have strongly
tested task and data control features (interactions \texttt{b} and
\texttt{c}), which would favor sub-tasking. The migration cost between
architectures has been ignored as well.

>>>>

Robustness is a highly desirable characteristic in production gateways. In this respect, the 
multiplicity of software components and interactions involved in architectures is
a challenge as it often leads to complex systems.
Architectures showing reduced system complexity will greatly
facilitate the implementation effort towards robust interactions
which, in turn, have a positive impact on characteristics such as
gateway predictability, transparence, general reliability and results
traceability and reproducibility; characteristics that are also key to
a good user experience. \closednote{Marc-Etienne}{I find that
  something is weak in this last paragraph. Robustness will help with
  transparency, sure, but it seems only a small facet.  Also, the text
  seem to timidly favor architectures with less
  components/interactions without much explanation... Complex systems
  can be robust, but at greater costs...  Here is one: "Architectures
  showing reduced system complexity will greatly facilitate the
  implementation effort towards robust interactions which, in turn,
  have a positive impact on characteristics such as gateway
  predictability, transparence, general reliability and results
  traceability and reproducibility; characteristics that are also key
  to a good user experience."}{Tristan}{Agreed, fixed as suggested.}

@@

Finally, the particular technical or historical context of a science
gateway project may obviously influence the choice of an architecture
to integrate workflow engines. For instance, some workflow engines may
be already available as web services, which would tend to favor
service invocation, and other science gateways may have strongly
tested task and data control features (interactions \texttt{b} and
\texttt{c}), which would favor sub-tasking. Similarly, adding a new
type of engine may facilitate integration of a new infrastructure when
interactions \texttt{b} and \texttt{c$_2$} are already available. The
migration cost between architectures has been ignored as well.
